---
title: "Prognostic Value of Remnant Cholesterol (RC) in Patients with MASLD"
author: An Tran
date: last-modified
format:
  docx:
    fig-dpi: 300
    fig-cap-location: "bottom"
    tbl-cap-location: "top"
execute:
  echo: false
  warning: false
  message: false
knitr:
  opts_chunk: 
    fig.path: "Figures/"
    dev: "jpeg"             
---

```{r}
#| label: setup
pacman::p_load(readxl, survey, survival, gtsummary, survminer, splines, mice, timeROC, 
               dplyr, ggplot2, ggsci, rms, tidycmprsk, tidyr, survIDINRI, tableone,
               patchwork, gt, forestploter, regplot, dcurves, car, dagitty, ggdag)

raw_df <- read_excel("data.xlsx", sheet = "RAW DATA")

df_step1 <- raw_df %>% 
  filter(RIDAGEYR >= 20) %>%
  filter(
    !is.na(LBXTR) & !is.na(LBDSGLSI) & !is.na(LBDHDD) & 
      !is.na(LBXSATSI) & !is.na(LBXSASSI) &               
      !is.na(BMXBMI) & !is.na(BMXWAIST) & !is.na(BMXWT) & !is.na(BMXHT) & 
      !is.na(WTSAF2YR) & WTSAF2YR > 0 
  )

df_step1 <- df_step1 %>%
  mutate(cvd_hx = ifelse(MCQ160B == 1 | MCQ160C == 1 | MCQ160E == 1 | MCQ160F == 1, 1, 0))

vars_to_impute <- c("INDFMPIR", "DMDEDUC2", "DMDMARTL", "LBXWBCSI", "LBXSCR", 
                    "LBXSUA", "cvd_hx", "diabetes", "hyperten")

cat_vars <- c("RIAGENDR", "RIDRETH1", "DMDEDUC2", "DMDMARTL", "diabetes", "hyperten", "cvd_hx")
df_step1[cat_vars] <- lapply(df_step1[cat_vars], as.factor)

imputed_data <- mice(df_step1[, vars_to_impute], m = 5, method = 'pmm', seed = 123, printFlag = FALSE)

df_imputed <- df_step1
df_imputed[, vars_to_impute] <- complete(imputed_data, 1)

df_imputed$diabetes <- as.numeric(as.character(df_imputed$diabetes))
df_imputed$hyperten <- as.numeric(as.character(df_imputed$hyperten))
```

```{r}
#| label: data-processing
df_final <- df_imputed %>%
  mutate(
    HSI = 8 * (LBXSATSI / LBXSASSI) + BMXBMI + ifelse(RIAGENDR == 2, 2, 0) + ifelse(diabetes == 1, 2, 0),
    steatosis = ifelse(HSI > 36, 1, 0),
    cm_risk = ifelse(
      BMXBMI >= 25 | (RIAGENDR == 1 & BMXWAIST >= 94) | (RIAGENDR == 2 & BMXWAIST >= 80) | 
        LBDSGLSI >= 5.55 | diabetes == 1 | hyperten == 1 | LBXTR >= 150 | 
        (RIAGENDR == 1 & LBDHDD < 40) | (RIAGENDR == 2 & LBDHDD < 50), 1, 0),
    
    is_masld = ifelse(steatosis == 1 & cm_risk == 1, 1, 0),
    
    TyHGB = (LBXTR / LBDHDD) + (0.7 * LBDSGLSI) + (0.1 * BMXBMI),
    
    ABSI = BMXWAIST / ((BMXBMI^(2/3)) * (BMXHT^(1/2))),
    WWI = BMXWAIST / sqrt(BMXWT),
    WHtR = BMXWAIST / BMXHT,
    
    # TẠO TỶ SỐ AST/ALT (Tránh đa cộng tuyến)
    AST_ALT_ratio = LBXSASSI / LBXSATSI,
    
    status_acm = ifelse(mortstat == 1, 1, 0),
    status_cvm = ifelse(mortstat == 1 & ucod_leading %in% c("001", "005"), 1, 0),
    time_months = permth_int
  ) %>%
  filter(is_masld == 1, (is.na(RIDEXPRG) | RIDEXPRG != 1), !is.na(mortstat), !is.na(time_months), eligstat == 1) %>%
  mutate(
    TyHGB_Q = factor(ntile(TyHGB, 4), labels = c("Q1", "Q2", "Q3", "Q4")),
    status_acm_factor = factor(status_acm),
    status_cvm_factor = factor(status_cvm),
    event_cr = case_when(mortstat == 0 ~ 0, status_cvm == 1 ~ 1, mortstat == 1 & status_cvm == 0 ~ 2)
  )

# TẠO SẴN CÁC BIẾN CHUẨN HÓA Z-SCORE CHO TOÀN BỘ CODE CÁC BƯỚC SAU
df_final <- df_final %>%
  mutate(
    TyHGB_Z = as.numeric(scale(TyHGB)),
    ABSI_Z  = as.numeric(scale(ABSI)),
    WWI_Z   = as.numeric(scale(WWI)),
    WHtR_Z  = as.numeric(scale(WHtR)),
    TyHGB_Q_num = as.numeric(TyHGB_Q)
  )

df_final <- df_final %>%
  mutate(
    DMDEDUC2 = case_when(
      DMDEDUC2 %in% c(1, 2) ~ "Under High School",
      DMDEDUC2 == 3 ~ "High School to University",
      DMDEDUC2 %in% c(4, 5) ~ "Above University",
      TRUE ~ NA_character_
    ),
    RIDRETH1 = case_when(
      RIDRETH1 == 3 ~ "Non-Hispanic White",
      RIDRETH1 == 4 ~ "Non-Hispanic Black",
      TRUE ~ "Other Races"
    )
  ) %>%
  drop_na(DMDEDUC2, RIDRETH1)

cat_vars_final <- c("RIAGENDR", "RIDRETH1", "DMDEDUC2", "cvd_hx")
df_final <- df_final %>% mutate(across(all_of(cat_vars_final), as.factor))

masld_design <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA, weights = ~WTSAF2YR, nest = TRUE, data = df_final)

covs_m2 <- "RIDAGEYR + RIAGENDR + RIDRETH1"
covs_m3 <- paste(covs_m2, "+ hyperten + AST_ALT_ratio")
covs_str <- covs_m3
```

## 1. Baseline characteristics

```{r}
#| label: tbl-baseline
#| tbl-cap: "Table 1: Baseline characteristics of the study population according to TyHGB quartiles"

vars_table1 <- c("RIDAGEYR", "RIAGENDR", "RIDRETH1", "DMDEDUC2", "INDFMPIR",
                 "BMXBMI", "BMXWAIST", "TyHGB", "ABSI", "WWI", "WHtR", 
                 "LBXTC", "LBXTR", "LBDHDD", "LBDSGLSI", "LBXSATSI", "LBXSASSI", "AST_ALT_ratio",
                 "LBXWBCSI", "LBXLYPCT", "LBXMOPCT", "LBXNEPCT", "LBXEOPCT", "LBXBAPCT",
                 "LBDLYMNO", "LBDMONO", "LBDNENO", "LBDEONO", "LBDBANO",
                 "LBXRBCSI", "LBXHGB", "LBXHCT", "diabetes", "hyperten", "cvd_hx", 
                 "status_acm_factor", "status_cvm_factor")

tab1_gt <- masld_design %>%
  tbl_svysummary(
    by = TyHGB_Q, 
    include = all_of(vars_table1),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})", 
      all_categorical() ~ "{n_unweighted} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 2, 
      all_categorical() ~ c(0, 1)
    ), 
    missing = "no",
    label = list(AST_ALT_ratio ~ "AST/ALT Ratio")
  ) %>%
  add_p() %>% 
  add_overall() %>%
  bold_labels()

tab1_gt
```

## 2. Covariate Selection (Multicollinearity Check & DAG)

```{r}
#| label: tbl-vif-dag
#| fig-cap: "Figure 1: Directed Acyclic Graph (DAG) and Variance Inflation Factor (VIF) confirming covariate selection"
#| fig-width: 10
#| fig-height: 6

f_vif_acm <- as.formula(paste("Surv(time_months, status_acm) ~ TyHGB +", covs_str))
f_vif_cvm <- as.formula(paste("Surv(time_months, status_cvm) ~ TyHGB +", covs_str))

fit_cox_acm <- svycoxph(f_vif_acm, design = masld_design)
fit_cox_cvm <- svycoxph(f_vif_cvm, design = masld_design)

vif_acm <- car::vif(fit_cox_acm)
vif_cvm <- car::vif(fit_cox_cvm)

cov_names <- rownames(vif_acm)

df_vif_acm <- data.frame(
  Covariate = cov_names, GVIF_ACM = sprintf("%.2f", vif_acm[, 1]), Df_ACM = vif_acm[, 2], Adj_GVIF_ACM = sprintf("%.2f", vif_acm[, 3])
)

df_vif_cvm <- data.frame(
  Covariate = cov_names, GVIF_CVM = sprintf("%.2f", vif_cvm[, 1]), Df_CVM = vif_cvm[, 2], Adj_GVIF_CVM = sprintf("%.2f", vif_cvm[, 3])
)

df_vif_combined <- merge(df_vif_acm, df_vif_cvm, by = "Covariate", sort = FALSE)

tbl_vif <- df_vif_combined %>% gt() %>%
  tab_header(title = "Variance Inflation Factor (VIF) for Final Models") %>%
  tab_spanner(label = "All-Cause Mortality (ACM)", columns = c(GVIF_ACM, Df_ACM, Adj_GVIF_ACM)) %>%
  tab_spanner(label = "Cardiovascular Mortality (CVM)", columns = c(GVIF_CVM, Df_CVM, Adj_GVIF_CVM)) %>%
  cols_label(GVIF_ACM = "GVIF", Df_ACM = "Df", Adj_GVIF_ACM = "GVIF^(1/2Df)", GVIF_CVM = "GVIF", Df_CVM = "Df", Adj_GVIF_CVM = "GVIF^(1/2Df)") %>%
  cols_align(align = "center") %>% cols_align(align = "left", columns = Covariate) %>%
  tab_options(heading.background.color = "#E8F4F0")

dag_model <- dagitty('dag {
  "Age" [pos="2,2"]
  "Gender" [pos="0.8,1.3"]
  "Race/Ethnicity" [pos="3.2,1.3"]
  "AST/ALT Ratio" [pos="1.2,-1.3"]
  "Hypertension" [pos="2.0,-2.0"]
  "TyHGB" [exposure, pos="0,0"]
  "Mortality" [outcome, pos="4,0"]
  
  "Age" -> "TyHGB"; "Age" -> "Mortality"
  "Gender" -> "TyHGB"; "Gender" -> "Mortality"
  "Race/Ethnicity" -> "TyHGB"; "Race/Ethnicity" -> "Mortality"
  "AST/ALT Ratio" -> "TyHGB"; "AST/ALT Ratio" -> "Mortality"
  "Hypertension" -> "TyHGB"; "Hypertension" -> "Mortality"
  "TyHGB" -> "Mortality"
}')

p_dag <- ggdag(dag_model, text = FALSE, use_labels = NULL) +
  geom_dag_edges(edge_color = "#D35400", edge_width = 0.8, arrow_directed = grid::arrow(length = grid::unit(0.12, "inches"), type = "closed")) +
  geom_dag_point(aes(color = name), size = 14) +
  geom_text(aes(label = name, x = x, y = y - 0.35), color = "black", fontface = "bold", size = 4.5) +
  scale_color_manual(values = c("TyHGB" = "#E64B35", "Mortality" = "#0055A4", "Age" = "#95A5A6", "Gender" = "#95A5A6", 
                                "Race/Ethnicity" = "#95A5A6", "AST/ALT Ratio" = "#95A5A6", "Hypertension" = "#95A5A6")) +
  scale_x_continuous(expand = expansion(mult = 0.15)) + scale_y_continuous(expand = expansion(mult = 0.2)) +
  theme_dag_blank() + theme(legend.position = "none")

tbl_vif
p_dag
```

## 3. Independent association of TyHGB with mortality (Stepwise Models)

```{r}
#| label: tbl-cox-tyhgb
#| tbl-cap: "Table 2: Cox regression analysis demonstrating the independent association of TyHGB with mortality"

mods <- list("Model 1 (Unadjusted)" = "", "Model 2 (Demographics)" = paste("+", covs_m2), "Model 3 (Fully Adjusted)" = paste("+", covs_str))

run_main_model <- function(event_var, outcome_name) {
  res_list <- list()
  for(m in names(mods)) {
    f_cont <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_Z", mods[[m]]))
    fit_cont <- svycoxph(f_cont, design = masld_design)
    sm_cont <- summary(fit_cont)
    hr_cont <- sprintf("%.3f (%.3f-%.3f)", sm_cont$conf.int["TyHGB_Z", 1], sm_cont$conf.int["TyHGB_Z", 3], sm_cont$conf.int["TyHGB_Z", 4])
    p_val_cont <- sm_cont$coef["TyHGB_Z", "Pr(>|z|)"]
    p_cont <- ifelse(p_val_cont < 0.001, "<0.001", sprintf("%.3f", p_val_cont))
    
    f_q <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_Q", mods[[m]]))
    fit_q <- svycoxph(f_q, design = masld_design)
    sm_q <- summary(fit_q)
    
    p_q2 <- sprintf("%.3f", sm_q$coef["TyHGB_QQ2", "Pr(>|z|)"])
    p_q3 <- sprintf("%.3f", sm_q$coef["TyHGB_QQ3", "Pr(>|z|)"])
    p_q4 <- sprintf("%.3f", sm_q$coef["TyHGB_QQ4", "Pr(>|z|)"])
    
    f_trend <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_Q_num", mods[[m]]))
    fit_trend <- svycoxph(f_trend, design = masld_design)
    p_val_trend <- summary(fit_trend)$coef["TyHGB_Q_num", "Pr(>|z|)"]
    p_trend <- ifelse(p_val_trend < 0.001, "<0.001", sprintf("%.3f", p_val_trend))
    
    res_list[[length(res_list)+1]] <- data.frame(
      Outcome = outcome_name, 
      TyHGB = c("Continuous (per 1-SD)", "Quartile 1", "Quartile 2", "Quartile 3", "Quartile 4", "P for trend"), 
      Model = m,
      `HR (95% CI)` = c(hr_cont, "Ref.", 
                        sprintf("%.3f (%.3f-%.3f)", sm_q$conf.int["TyHGB_QQ2", 1], sm_q$conf.int["TyHGB_QQ2", 3], sm_q$conf.int["TyHGB_QQ2", 4]),
                        sprintf("%.3f (%.3f-%.3f)", sm_q$conf.int["TyHGB_QQ3", 1], sm_q$conf.int["TyHGB_QQ3", 3], sm_q$conf.int["TyHGB_QQ3", 4]),
                        sprintf("%.3f (%.3f-%.3f)", sm_q$conf.int["TyHGB_QQ4", 1], sm_q$conf.int["TyHGB_QQ4", 3], sm_q$conf.int["TyHGB_QQ4", 4]), ""),
      `P value` = c(p_cont, "-", p_q2, p_q3, p_q4, p_trend), check.names = FALSE
    )
  }
  bind_rows(res_list)
}

df_main_tbl <- bind_rows(run_main_model("status_acm", "All-Cause Mortality"), run_main_model("status_cvm", "Cardiovascular Mortality")) %>% 
  tidyr::pivot_wider(names_from = Model, values_from = c(`HR (95% CI)`, `P value`))

df_main_tbl %>% 
  select(Outcome, TyHGB, contains("Model 1"), contains("Model 2"), contains("Model 3")) %>% 
  gt(groupname_col = "Outcome") %>% 
  tab_options(row_group.font.weight = "bold", row_group.background.color = "#F0F0F0") %>%
  cols_align(align = "center") %>% cols_align(align = "left", columns = 1)
```

## 4. Sensitivity Analysis (Excluding deaths within 24 months)

```{r}
#| label: tbl-sens
#| tbl-cap: "Supplemental Table 1: Association between TyHGB and mortality excluding early events (Addressing Reverse Causation)"

options(survey.lonely.psu = "adjust")
des_sens <- subset(masld_design, time_months > 24)

run_sens_model <- function(event_var, outcome_name) {
  res_list <- list()
  for(m in names(mods)) {
    f_cont <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_Z", mods[[m]]))
    fit_cont <- svycoxph(f_cont, design = des_sens)
    sm_cont <- summary(fit_cont)
    hr_cont <- sprintf("%.3f (%.3f-%.3f)", sm_cont$conf.int["TyHGB_Z", 1], sm_cont$conf.int["TyHGB_Z", 3], sm_cont$conf.int["TyHGB_Z", 4])
    p_val_cont <- sm_cont$coef["TyHGB_Z", "Pr(>|z|)"]
    p_cont <- ifelse(p_val_cont < 0.001, "<0.001", sprintf("%.3f", p_val_cont))
    
    f_q <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_Q", mods[[m]]))
    fit_q <- svycoxph(f_q, design = des_sens)
    sm_q <- summary(fit_q)
    
    p_q2 <- sprintf("%.3f", sm_q$coef["TyHGB_QQ2", "Pr(>|z|)"])
    p_q3 <- sprintf("%.3f", sm_q$coef["TyHGB_QQ3", "Pr(>|z|)"])
    p_q4 <- sprintf("%.3f", sm_q$coef["TyHGB_QQ4", "Pr(>|z|)"])
    
    f_trend <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_Q_num", mods[[m]]))
    fit_trend <- svycoxph(f_trend, design = des_sens)
    p_val_trend <- summary(fit_trend)$coef["TyHGB_Q_num", "Pr(>|z|)"]
    p_trend <- ifelse(p_val_trend < 0.001, "<0.001", sprintf("%.3f", p_val_trend))
    
    res_list[[length(res_list)+1]] <- data.frame(
      Outcome = outcome_name, TyHGB = c("Continuous (per 1-SD)", "Quartile 1", "Quartile 2", "Quartile 3", "Quartile 4", "P for trend"), Model = m,
      `HR (95% CI)` = c(hr_cont, "Ref.", 
                        sprintf("%.3f (%.3f-%.3f)", sm_q$conf.int["TyHGB_QQ2", 1], sm_q$conf.int["TyHGB_QQ2", 3], sm_q$conf.int["TyHGB_QQ2", 4]),
                        sprintf("%.3f (%.3f-%.3f)", sm_q$conf.int["TyHGB_QQ3", 1], sm_q$conf.int["TyHGB_QQ3", 3], sm_q$conf.int["TyHGB_QQ3", 4]),
                        sprintf("%.3f (%.3f-%.3f)", sm_q$conf.int["TyHGB_QQ4", 1], sm_q$conf.int["TyHGB_QQ4", 3], sm_q$conf.int["TyHGB_QQ4", 4]), ""),
      `P value` = c(p_cont, "-", p_q2, p_q3, p_q4, p_trend), check.names = FALSE
    )
  }
  bind_rows(res_list)
}

df_sens_tbl <- bind_rows(run_sens_model("status_acm", "All-Cause Mortality"), run_sens_model("status_cvm", "Cardiovascular Mortality")) %>% tidyr::pivot_wider(names_from = Model, values_from = c(`HR (95% CI)`, `P value`))
df_sens_tbl %>% select(Outcome, TyHGB, contains("Model 1"), contains("Model 2"), contains("Model 3")) %>% gt(groupname_col = "Outcome") %>% tab_options(row_group.font.weight = "bold", row_group.background.color = "#F0F0F0") %>% cols_align(align = "center") %>% cols_align(align = "left", columns = 1)
```

## 5. Competing Risk Analysis (Fine-Gray Model)

```{r}
#| label: tbl-finegray
#| tbl-cap: "Table 3: Competing risk analysis (Fine-Gray model) for cardiovascular mortality comparing multiple indices"

df_fg <- df_final[, c("time_months", "event_cr", "SDMVPSU", "SDMVSTRA", "WTSAF2YR", 
                      "TyHGB_Z", "ABSI_Z", "WWI_Z", "WHtR_Z", 
                      "RIDAGEYR", "RIAGENDR", "RIDRETH1", "hyperten", "AST_ALT_ratio")]
df_fg$event_cr_fg <- factor(df_fg$event_cr, levels = c(0, 1, 2), labels = c("censor", "CVM", "Other_Death"))

fg_data <- finegray(Surv(time_months, event_cr_fg) ~ ., data = df_fg, etype = "CVM")
fg_design <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA, weights = ~WTSAF2YR * fgwt, nest = TRUE, data = fg_data)

markers <- c("TyHGB_Z", "ABSI_Z", "WWI_Z", "WHtR_Z")

get_fg_res <- function(marker) {
  form_uni <- paste0("Surv(fgstart, fgstop, fgstatus) ~ ", marker)
  fit_uni <- suppressWarnings(svycoxph(as.formula(form_uni), design = fg_design))
  res_uni <- tidy(fit_uni, exponentiate = TRUE, conf.int = TRUE) %>% filter(term == marker)
  sHR_uni <- sprintf("%.3f (%.3f-%.3f)", res_uni$estimate, res_uni$conf.low, res_uni$conf.high)
  p_uni <- ifelse(res_uni$p.value < 0.001, "<0.001", sprintf("%.3f", res_uni$p.value))
  
  form_multi <- paste0("Surv(fgstart, fgstop, fgstatus) ~ ", marker, " + ", covs_str)
  fit_multi <- suppressWarnings(svycoxph(as.formula(form_multi), design = fg_design))
  res_multi <- tidy(fit_multi, exponentiate = TRUE, conf.int = TRUE) %>% filter(term == marker)
  sHR_multi <- sprintf("%.3f (%.3f-%.3f)", res_multi$estimate, res_multi$conf.low, res_multi$conf.high)
  p_multi <- ifelse(res_multi$p.value < 0.001, "<0.001", sprintf("%.3f", res_multi$p.value))
  
  return(c(sHR_uni, p_uni, sHR_multi, p_multi))
}

results_fg <- list()
for (marker in markers) {
  res <- get_fg_res(marker)
  results_fg[[length(results_fg) + 1]] <- data.frame(
    Marker = gsub("_Z", "", marker), Uni_sHR = res[1], Uni_P = res[2], Multi_sHR = res[3], Multi_P = res[4], stringsAsFactors = FALSE
  )
}
df_fg_final <- bind_rows(results_fg)

table_fg_gt <- df_fg_final %>%
  gt() %>%
  tab_spanner(label = md("**Univariate analysis (per 1-SD increase)**"), columns = c(Uni_sHR, Uni_P)) %>%
  tab_spanner(label = md("**Multivariate Analysis (per 1-SD increase)**"), columns = c(Multi_sHR, Multi_P)) %>%
  cols_label(Marker = "", Uni_sHR = md("**sHR (95% CIs)**"), Uni_P = md("**p-value**"), Multi_sHR = md("**sHR (95% CIs)**"), Multi_P = md("**p-value**")) %>%
  tab_options(column_labels.font.weight = "bold", table.border.top.color = "black", table.border.bottom.color = "black", table_body.border.bottom.color = "black") %>%
  cols_align(align = "left", columns = everything())
table_fg_gt
```

## 6. Kaplan-Meier survival analysis

```{r}
#| label: fig-km
#| fig-cap: "Figure 2: Kaplan-Meier survival curves comparing combining TyHGB with obesity indices"
#| fig-width: 18
#| fig-height: 10

cox_acm_m1 <- svycoxph(as.formula(paste("Surv(time_months, status_acm) ~ TyHGB +", covs_str)), design = masld_design)
cox_acm_m2 <- svycoxph(as.formula(paste("Surv(time_months, status_acm) ~ TyHGB + ABSI +", covs_str)), design = masld_design)
cox_acm_m3 <- svycoxph(as.formula(paste("Surv(time_months, status_acm) ~ TyHGB + WWI +", covs_str)), design = masld_design)
cox_acm_m4 <- svycoxph(as.formula(paste("Surv(time_months, status_acm) ~ TyHGB + WHtR +", covs_str)), design = masld_design)

cox_cvm_m1 <- svycoxph(as.formula(paste("Surv(time_months, status_cvm) ~ TyHGB +", covs_str)), design = masld_design)
cox_cvm_m2 <- svycoxph(as.formula(paste("Surv(time_months, status_cvm) ~ TyHGB + ABSI +", covs_str)), design = masld_design)
cox_cvm_m3 <- svycoxph(as.formula(paste("Surv(time_months, status_cvm) ~ TyHGB + WWI +", covs_str)), design = masld_design)
cox_cvm_m4 <- svycoxph(as.formula(paste("Surv(time_months, status_cvm) ~ TyHGB + WHtR +", covs_str)), design = masld_design)

df_final <- df_final %>%
  mutate(
    lp_acm_m1 = predict(cox_acm_m1, type="lp"), Q_acm_m1 = factor(ntile(lp_acm_m1, 4), labels=paste0("Q", 1:4)),
    lp_acm_m2 = predict(cox_acm_m2, type="lp"), Q_acm_m2 = factor(ntile(lp_acm_m2, 4), labels=paste0("Q", 1:4)),
    lp_acm_m3 = predict(cox_acm_m3, type="lp"), Q_acm_m3 = factor(ntile(lp_acm_m3, 4), labels=paste0("Q", 1:4)),
    lp_acm_m4 = predict(cox_acm_m4, type="lp"), Q_acm_m4 = factor(ntile(lp_acm_m4, 4), labels=paste0("Q", 1:4)),
    
    lp_cvm_m1 = predict(cox_cvm_m1, type="lp"), Q_cvm_m1 = factor(ntile(lp_cvm_m1, 4), labels=paste0("Q", 1:4)),
    lp_cvm_m2 = predict(cox_cvm_m2, type="lp"), Q_cvm_m2 = factor(ntile(lp_cvm_m2, 4), labels=paste0("Q", 1:4)),
    lp_cvm_m3 = predict(cox_cvm_m3, type="lp"), Q_cvm_m3 = factor(ntile(lp_cvm_m3, 4), labels=paste0("Q", 1:4)),
    lp_cvm_m4 = predict(cox_cvm_m4, type="lp"), Q_cvm_m4 = factor(ntile(lp_cvm_m4, 4), labels=paste0("Q", 1:4))
  )
masld_design <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA, weights = ~WTSAF2YR, nest = TRUE, data = df_final)

create_km <- function(group_var, event_var, model_name) {
  form_svy <- as.formula(paste("Surv(time_months,", event_var, ") ~", group_var))
  res_logrank <- svylogrank(form_svy, design = masld_design)
  p_val <- if(!is.null(res_logrank$p.value)) res_logrank$p.value else pchisq(res_logrank[[2]][1], res_logrank[[2]][2], lower.tail = FALSE)
  p_str <- if(is.na(p_val)) "Weighted P: N/A" else if(p_val < 0.001) "Weighted P < 0.001" else paste0("Weighted P = ", round(p_val, 3))
  
  fit <- eval(parse(text = paste0("survfit(Surv(time_months, ", event_var, ") ~ ", group_var, ", data = df_final)")))
  my_palette <- c("#4daf4a", "#d95f02", "#7570b3", "#984ea3") 
  
  p <- ggsurvplot(
    fit, data = df_final, palette = my_palette, linewidth = 1, title = "", legend.title = model_name,                
    legend.labs = c("Q1", "Q2", "Q3", "Q4"), xlab = "Months", ylab = "Survival Probability",
    pval = p_str, pval.size = 4, conf.int = TRUE, conf.int.style = "ribbon", conf.int.alpha = 0.15,                    
    censor = FALSE, risk.table = TRUE, risk.table.height = 0.28, fontsize = 3.5, ggtheme = theme_classic()
  )
  p$plot <- p$plot + theme(legend.title = element_text(face = "bold", size = 11))
  p$table <- p$table + theme(axis.title.y = element_blank())
  return(p)
}

combine_km <- function(km_obj) {
  km_obj$table <- km_obj$table + theme(axis.title.y = element_blank())
  (km_obj$plot / km_obj$table) + plot_layout(heights = c(3, 1))
}

pw_acm1 <- combine_km(create_km("Q_acm_m1", "status_acm", "TyHGB"))
pw_acm2 <- combine_km(create_km("Q_acm_m2", "status_acm", "TyHGB + ABSI"))
pw_acm3 <- combine_km(create_km("Q_acm_m3", "status_acm", "TyHGB + WWI"))
pw_acm4 <- combine_km(create_km("Q_acm_m4", "status_acm", "TyHGB + WHtR"))

pw_cvm1 <- combine_km(create_km("Q_cvm_m1", "status_cvm", "TyHGB"))
pw_cvm2 <- combine_km(create_km("Q_cvm_m2", "status_cvm", "TyHGB + ABSI"))
pw_cvm3 <- combine_km(create_km("Q_cvm_m3", "status_cvm", "TyHGB + WWI"))
pw_cvm4 <- combine_km(create_km("Q_cvm_m4", "status_cvm", "TyHGB + WHtR"))

final_plot <- (pw_acm1 | pw_acm2 | pw_acm3 | pw_acm4) / (pw_cvm1 | pw_cvm2 | pw_cvm3 | pw_cvm4)
final_plot
```

## 7. Time-dependent ROC Curves

```{r}
#| label: fig-roc
#| fig-cap: "Figure 3: Time-dependent ROC curves comparing combinations of TyHGB and other obesity indices"
#| fig-width: 10
#| fig-height: 7

roc_a1 <- timeROC(T=df_final$time_months, delta=df_final$status_acm, marker=df_final$lp_acm_m1, cause=1, weighting="marginal", times=c(36,60,120))
roc_a2 <- timeROC(T=df_final$time_months, delta=df_final$status_acm, marker=df_final$lp_acm_m2, cause=1, weighting="marginal", times=c(36,60,120))
roc_a3 <- timeROC(T=df_final$time_months, delta=df_final$status_acm, marker=df_final$lp_acm_m3, cause=1, weighting="marginal", times=c(36,60,120))
roc_a4 <- timeROC(T=df_final$time_months, delta=df_final$status_acm, marker=df_final$lp_acm_m4, cause=1, weighting="marginal", times=c(36,60,120))

roc_c1 <- timeROC(T=df_final$time_months, delta=df_final$event_cr, marker=df_final$lp_cvm_m1, cause=1, weighting="marginal", times=c(36,60,120))
roc_c2 <- timeROC(T=df_final$time_months, delta=df_final$event_cr, marker=df_final$lp_cvm_m2, cause=1, weighting="marginal", times=c(36,60,120))
roc_c3 <- timeROC(T=df_final$time_months, delta=df_final$event_cr, marker=df_final$lp_cvm_m3, cause=1, weighting="marginal", times=c(36,60,120))
roc_c4 <- timeROC(T=df_final$time_months, delta=df_final$event_cr, marker=df_final$lp_cvm_m4, cause=1, weighting="marginal", times=c(36,60,120))

plot_roc <- function(r1, r2, r3, r4, time_idx, title) {
  get_roc_data <- function(roc_obj) {
    n <- names(roc_obj)
    auc_nm <- if("AUC" %in% n) "AUC" else if("AUC_1" %in% n) "AUC_1" else grep("^AUC", n, value=TRUE)[1]
    fp_nm  <- if("FP" %in% n) "FP" else if("FP_1" %in% n) "FP_1" else grep("^FP", n, value=TRUE)[1]
    tp_nm  <- if("TP" %in% n) "TP" else if("TP_1" %in% n) "TP_1" else grep("^TP", n, value=TRUE)[1]
    
    auc_val <- if(!is.null(auc_nm) && !is.na(auc_nm)) roc_obj[[auc_nm]] else rep(NA, 10)
    fp_val  <- if(!is.null(fp_nm) && !is.na(fp_nm)) roc_obj[[fp_nm]] else matrix(NA, nrow=10, ncol=10)
    tp_val  <- if(!is.null(tp_nm) && !is.na(tp_nm)) roc_obj[[tp_nm]] else matrix(NA, nrow=10, ncol=10)
    if(is.null(auc_val) || length(auc_val) == 0) auc_val <- rep(NA, 10)
    return(list(AUC = auc_val, FP = fp_val, TP = tp_val))
  }
  
  d1 <- get_roc_data(r1); d2 <- get_roc_data(r2); d3 <- get_roc_data(r3); d4 <- get_roc_data(r4)
  
  df_roc <- data.frame(
    FPR = c(d1$FP[,time_idx], d2$FP[,time_idx], d3$FP[,time_idx], d4$FP[,time_idx]),
    TPR = c(d1$TP[,time_idx], d2$TP[,time_idx], d3$TP[,time_idx], d4$TP[,time_idx]),
    Model = c(
      rep(paste0("TyHGB (AUC=", round(d1$AUC[time_idx], 3), ")"), length(d1$FP[,time_idx])),
      rep(paste0("TyHGB+ABSI (AUC=", round(d2$AUC[time_idx], 3), ")"), length(d2$FP[,time_idx])),
      rep(paste0("TyHGB+WWI (AUC=", round(d3$AUC[time_idx], 3), ")"), length(d3$FP[,time_idx])),
      rep(paste0("TyHGB+WHtR (AUC=", round(d4$AUC[time_idx], 3), ")"), length(d4$FP[,time_idx]))
    )
  )
  
  ggplot(df_roc, aes(x = FPR, y = TPR, color = Model)) +
    geom_line(linewidth = 1) + 
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray50") +
    scale_color_nejm() + theme_bw() +
    theme(legend.position = c(0.65, 0.22), legend.title = element_blank(),
          legend.background = element_rect(fill = alpha("white", 0.7), color = "black"),
          legend.text = element_text(size = 9, face = "bold"), title = element_text(size = 12, face = "bold")) +
    labs(title = title, x = "1 - Specificity", y = "Sensitivity")
}

hide_x <- theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
hide_y <- theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())

p_roc_a1 <- plot_roc(roc_a1, roc_a2, roc_a3, roc_a4, 1, "ACM - 3 Years") + hide_x
p_roc_a2 <- plot_roc(roc_a1, roc_a2, roc_a3, roc_a4, 2, "ACM - 5 Years") + hide_x + hide_y
p_roc_a3 <- plot_roc(roc_a1, roc_a2, roc_a3, roc_a4, 3, "ACM - 10 Years") + hide_x + hide_y
p_roc_c1 <- plot_roc(roc_c1, roc_c2, roc_c3, roc_c4, 1, "CVM - 3 Years")
p_roc_c2 <- plot_roc(roc_c1, roc_c2, roc_c3, roc_c4, 2, "CVM - 5 Years") + hide_y
p_roc_c3 <- plot_roc(roc_c1, roc_c2, roc_c3, roc_c4, 3, "CVM - 10 Years") + hide_y

final_roc_plot <- (p_roc_a1 | p_roc_a2 | p_roc_a3) / (p_roc_c1 | p_roc_c2 | p_roc_c3)
final_roc_plot
```

## 8. Incremental predictive value (IDI / NRI)

```{r}
#| label: tbl-incremental
#| tbl-cap: "Table 4: Incremental predictive value of adding TyHGB and combined indices to the base clinical model"

cox_acm_base <- svycoxph(as.formula(paste("Surv(time_months, status_acm) ~", covs_str)), design = masld_design)
cox_cvm_base <- svycoxph(as.formula(paste("Surv(time_months, status_cvm) ~", covs_str)), design = masld_design)

df_final$lp_acm_base <- predict(cox_acm_base, type="lp")
df_final$lp_cvm_base <- predict(cox_cvm_base, type="lp")

get_c_ci <- function(time_var, event_var, lp_var, weights_var) {
  c_obj <- concordance(Surv(time_var, event_var) ~ lp_var, weights = weights_var)
  c_val <- ifelse(c_obj$concordance < 0.5, 1 - c_obj$concordance, c_obj$concordance)
  se <- sqrt(c_obj$var)
  lower <- c_val - 1.96 * se
  upper <- c_val + 1.96 * se
  return(list(c_str = paste0(sprintf("%.3f", c_val), " (", sprintf("%.3f", lower), "-", sprintf("%.3f", upper), ")"), 
              c_val = c_val, se = se))
}

compare_models <- function(time_var, event_var, event_cr_var, lp_base, lp_new, weights_var, t0, is_cvm) {
  
  base_c <- get_c_ci(time_var, event_var, lp_base, weights_var)
  new_c  <- get_c_ci(time_var, event_var, lp_new, weights_var)
  
  if(is_cvm) { 
    roc_base <- timeROC(T=time_var, delta=event_cr_var, marker=lp_base, cause=1, weighting="marginal", times=t0, iid=TRUE)
    roc_new  <- timeROC(T=time_var, delta=event_cr_var, marker=lp_new, cause=1, weighting="marginal", times=t0, iid=TRUE)
  } else {
    roc_base <- timeROC(T=time_var, delta=event_var, marker=lp_base, cause=1, weighting="marginal", times=t0, iid=TRUE)
    roc_new  <- timeROC(T=time_var, delta=event_var, marker=lp_new, cause=1, weighting="marginal", times=t0, iid=TRUE)
  }
  
  comp_res <- compare(roc_new, roc_base, adjusted=FALSE)
  p_delong <- if(!is.null(comp_res$p_values_AUC)) comp_res$p_values_AUC[1] else comp_res$p_values_AUC_1[1]
  
  if(is.na(p_delong)) {
    se_diff <- sqrt(base_c$se^2 + new_c$se^2)
    if (se_diff == 0) se_diff <- 1e-6 
    z_stat <- abs(new_c$c_val - base_c$c_val) / se_diff
    p_delong <- 2 * (1 - pnorm(z_stat))
  }
  
  indata_df <- data.frame(time = time_var, status = event_var)
  
  set.seed(123)
  idi_res <- IDI.INF(indata_df, covs0 = as.matrix(lp_base), covs1 = as.matrix(lp_new), t0 = t0, npert = 100) 
  out_matrix <- IDI.INF.OUT(idi_res)
  
  idi_str <- paste0(sprintf("%.3f", out_matrix[1, 1]), " (", sprintf("%.3f", out_matrix[1, 2]), "-", sprintf("%.3f", out_matrix[1, 3]), ")")
  idi_p   <- out_matrix[1, 4]
  
  nri_str <- paste0(sprintf("%.3f", out_matrix[3, 1]), " (", sprintf("%.3f", out_matrix[3, 2]), "-", sprintf("%.3f", out_matrix[3, 3]), ")")
  nri_p   <- out_matrix[3, 4]
  
  return(list(c_new = new_c$c_str, p_delong = p_delong, nri = nri_str, p_nri = nri_p, idi = idi_str, p_idi = idi_p))
}

run_all_comparisons <- function(time_var, event_var, event_cr_var, lp_base, lp_m1, lp_m2, lp_m3, lp_m4, weights_var, t0 = 120, is_cvm = FALSE, outcome_name) {
  cat(paste("\n================ KẾT QUẢ CHO:", outcome_name, "================\n"))
  
  c_base_str <- get_c_ci(time_var, event_var, lp_base, weights_var)$c_str
  cat(sprintf("Base Model (No TyHGB) - C-index: %s\n\n", c_base_str))
  
  cat(sprintf("%-15s | %-19s | %-8s | %-19s | %-8s | %-19s | %-8s\n",
              "Adding to Base", "C-index New (95%CI)", "P DeLong", "Cont. NRI (95%CI)", "P (NRI)", "IDI (95%CI)", "P (IDI)"))
  cat(strrep("-", 108), "\n")
  
  models <- list(
    list(name = "+ TyHGB",         lp = lp_m1),
    list(name = "+ TyHGB + ABSI",  lp = lp_m2),
    list(name = "+ TyHGB + WWI",   lp = lp_m3),
    list(name = "+ TyHGB + WHtR",  lp = lp_m4)
  )
  
  for (m in models) {
    res <- compare_models(time_var, event_var, event_cr_var, lp_base, m$lp, weights_var, t0, is_cvm)
    p_dl_print <- ifelse(res$p_delong < 0.001, "<0.001", sprintf("%.4f", res$p_delong))
    p_nri_print <- ifelse(res$p_nri < 0.001, "<0.001", sprintf("%.4f", res$p_nri))
    p_idi_print <- ifelse(res$p_idi < 0.001, "<0.001", sprintf("%.4f", res$p_idi))
    
    cat(sprintf("%-15s | %-19s | %-8s | %-19s | %-8s | %-19s | %-8s\n",
                m$name, res$c_new, p_dl_print, res$nri, p_nri_print, res$idi, p_idi_print))
  }
  cat("\n")
}

run_all_comparisons(
  time_var     = df_final$time_months, 
  event_var    = df_final$status_acm, 
  event_cr_var = df_final$status_acm,
  lp_base      = df_final$lp_acm_base,
  lp_m1        = df_final$lp_acm_m1,      
  lp_m2        = df_final$lp_acm_m2, 
  lp_m3        = df_final$lp_acm_m3, 
  lp_m4        = df_final$lp_acm_m4, 
  weights_var  = df_final$WTSAF2YR,
  t0           = 120, 
  is_cvm       = FALSE, 
  outcome_name = "ALL-CAUSE MORTALITY (ACM) TẠI 10 NĂM"
)

run_all_comparisons(
  time_var     = df_final$time_months, 
  event_var    = df_final$status_cvm, 
  event_cr_var = df_final$event_cr,
  lp_base      = df_final$lp_cvm_base,
  lp_m1        = df_final$lp_cvm_m1,      
  lp_m2        = df_final$lp_cvm_m2, 
  lp_m3        = df_final$lp_cvm_m3, 
  lp_m4        = df_final$lp_cvm_m4, 
  weights_var  = df_final$WTSAF2YR,
  t0           = 120, 
  is_cvm       = TRUE, 
  outcome_name = "CARDIOVASCULAR MORTALITY (CVM) TẠI 10 NĂM"
)
```

## 9. Dose-response relationship (RCS)

```{r}
#| label: fig-rcs
#| fig-cap: "Figure 4: Restricted cubic spline (RCS) curves showing the dose-response relationship between TyHGB index and mortality"
#| fig-width: 16
#| fig-height: 7

rcs_vars <- c("time_months", "status_acm", "status_cvm", "TyHGB", 
              "RIDAGEYR", "RIAGENDR", "RIDRETH1", "hyperten", "AST_ALT_ratio", "WTSAF2YR")

df_rcs <- na.omit(df_final[, rcs_vars])
dd <- datadist(df_rcs)
options(datadist = "dd")

plot_rcs_exact_style <- function(event_var, title_str) {
  form <- as.formula(paste("Surv(time_months, ", event_var, ") ~ rcs(TyHGB, 4) +", covs_str))
  fit <- cph(form, data = df_rcs, x = TRUE, y = TRUE, weights = df_rcs$WTSAF2YR)
  
  anv <- anova(fit)
  p_overall <- anv["TyHGB", "P"]
  p_nonlin  <- anv[" Nonlinear", "P"] 
  
  p_overall_str <- ifelse(p_overall < 0.001, "< 0.001", sprintf("%.3f", p_overall))
  p_nonlin_str  <- ifelse(p_nonlin < 0.001, "< 0.001", sprintf("%.3f", p_nonlin))
  knots_array <- fit$Design$parms$TyHGB
  knots_str <- paste(round(knots_array, 2), collapse = ", ")
  
  anno_text <- paste0("P-overall ", ifelse(p_overall < 0.001, "", "= "), p_overall_str, "\n",
                      "P-non-linear ", ifelse(p_nonlin < 0.001, "", "= "), p_nonlin_str, "\n",
                      "Knots: ", knots_str)
  
  pred <- rms::Predict(fit, TyHGB, fun = exp, ref.zero = TRUE)
  df_pred <- as.data.frame(pred)
  min_x <- min(df_rcs$TyHGB, na.rm = TRUE)
  max_x <- quantile(df_rcs$TyHGB, 0.99, na.rm = TRUE) 
  upper_limit_y <- 1.5
  max_dens <- max(density(df_rcs$TyHGB, na.rm = TRUE)$y)
  scale_factor <- max_dens / (upper_limit_y * 0.5) 
  df_knots <- data.frame(k = knots_array)
 
  p <- ggplot() +
    geom_histogram(data = df_rcs, aes(x = TyHGB, y = after_stat(density) / scale_factor), bins = 60, fill = "lightblue", color = "white", alpha = 0.9) +
    geom_line(data = df_pred, aes(x = TyHGB, y = lower), color = "black", linewidth = 1.5) +
    geom_line(data = df_pred, aes(x = TyHGB, y = upper), color = "black", linewidth = 1.5) +
    geom_line(data = df_pred, aes(x = TyHGB, y = yhat), color = "red", linewidth = 1) +
    geom_segment(data = df_knots, aes(x = k, xend = k, y = 0, yend = upper_limit_y * 0.02), color = "blue", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "black", linewidth = 0.6) +
    annotate("text", x = Inf, y = -Inf, label = anno_text, hjust = 1.05, vjust = -0.5, size = 4.5, color = "black") +
    coord_cartesian(xlim = c(min_x, max_x), ylim = c(0, upper_limit_y)) +
    scale_y_continuous(name = "Hazard Ratio (95% CI)", breaks = seq(0, 1.5, by = 0.5), sec.axis = sec_axis(~ . * scale_factor, name = "Probability Density")) +
    theme_bw() + labs(title = title_str, x = "TyHGB Index") +
    theme(plot.title = element_text(size = 14, face = "bold"),
          axis.title.y.left = element_text(size = 12), axis.text.y.left = element_text(size = 11),
          axis.title.y.right = element_text(size = 12), axis.text.y.right = element_text(size = 11),
          axis.title.x = element_text(size = 12), axis.text.x = element_text(size = 11),
          panel.grid.minor = element_blank(), panel.grid.major.x = element_line(linetype = "dotted", color = "gray80"))
  return(p)
}

p_rcs_acm <- plot_rcs_exact_style("status_acm", "")
p_rcs_cvm <- plot_rcs_exact_style("status_cvm", "")
final_rcs_plot <- (p_rcs_acm | p_rcs_cvm) + plot_annotation(tag_levels = 'A', tag_prefix = '(', tag_suffix = ')') & theme(plot.tag = element_text(size = 22, face = "bold")) 
final_rcs_plot
```

## 10. Threshold Effect Analysis (Two-piecewise Cox Model)

```{r}
#| label: tbl-threshold
#| tbl-cap: "Table 5: Threshold effect analysis and Dichotomized HR of TyHGB on ACM and CVM"

find_inflection <- function(event_var) {
  search_grid <- seq(quantile(df_final$TyHGB, 0.15), quantile(df_final$TyHGB, 0.85), length.out = 30)
  best_k <- NA; best_ll <- -Inf
  
  for(k in search_grid) {
    d_temp <- df_final %>% mutate(T1 = ifelse(TyHGB < k, TyHGB, k), T2 = ifelse(TyHGB >= k, TyHGB - k, 0))
    des <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA, weights = ~WTSAF2YR, nest = TRUE, data = d_temp)
    form <- as.formula(paste("Surv(time_months, ", event_var, ") ~ T1 + T2 +", covs_str))
    fit <- suppressWarnings(tryCatch(svycoxph(form, design = des), error = function(e) NULL))
    if(!is.null(fit) && fit$ll[2] > best_ll) { best_ll <- fit$ll[2]; best_k <- k }
  }
  return(best_k)
}

run_piecewise <- function(event_var, outcome_name) {
  k <- find_inflection(event_var)
  
  d_opt <- df_final %>% 
    mutate(
      T1 = ifelse(TyHGB < k, TyHGB, k), 
      T2 = ifelse(TyHGB >= k, TyHGB - k, 0),
      TyHGB_High = ifelse(TyHGB >= k, 1, 0)
    )
  des_opt <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA, weights = ~WTSAF2YR, nest = TRUE, data = d_opt)
  
  fit_lin <- svycoxph(as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB +", covs_str)), design = des_opt)
  sm_lin <- summary(fit_lin)
  hr_lin <- sprintf("%.3f (%.3f-%.3f)", sm_lin$conf.int["TyHGB", 1], sm_lin$conf.int["TyHGB", 3], sm_lin$conf.int["TyHGB", 4])
  p_val_lin <- sm_lin$coefficients["TyHGB", "Pr(>|z|)"]
  p_lin <- ifelse(p_val_lin < 0.001, "<0.001", sprintf("%.3f", p_val_lin))
  
  fit_pw <- svycoxph(as.formula(paste("Surv(time_months, ", event_var, ") ~ T1 + T2 +", covs_str)), design = des_opt)
  sm_pw <- summary(fit_pw)
  
  hr_t1 <- sprintf("%.3f (%.3f-%.3f)", sm_pw$conf.int["T1", 1], sm_pw$conf.int["T1", 3], sm_pw$conf.int["T1", 4])
  p_val_t1 <- sm_pw$coefficients["T1", "Pr(>|z|)"]
  p_t1 <- ifelse(p_val_t1 < 0.001, "<0.001", sprintf("%.3f", p_val_t1))
  
  hr_t2 <- sprintf("%.3f (%.3f-%.3f)", sm_pw$conf.int["T2", 1], sm_pw$conf.int["T2", 3], sm_pw$conf.int["T2", 4])
  p_val_t2 <- sm_pw$coefficients["T2", "Pr(>|z|)"]
  p_t2 <- ifelse(p_val_t2 < 0.001, "<0.001", sprintf("%.3f", p_val_t2))
  
  lrt_p <- 1 - pchisq(2 * (fit_pw$ll[2] - fit_lin$ll[2]), df = 1)
  lrt_p_str <- ifelse(lrt_p < 0.001, "<0.001", sprintf("%.3f", lrt_p))
  
  fit_bin <- svycoxph(as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_High +", covs_str)), design = des_opt)
  sm_bin <- summary(fit_bin)
  hr_bin <- sprintf("%.3f (%.3f-%.3f)", sm_bin$conf.int["TyHGB_High", 1], sm_bin$conf.int["TyHGB_High", 3], sm_bin$conf.int["TyHGB_High", 4])
  p_val_bin <- sm_bin$coefficients["TyHGB_High", "Pr(>|z|)"]
  p_bin <- ifelse(p_val_bin < 0.001, "<0.001", sprintf("%.3f", p_val_bin))
  
  event_t1 <- sum(d_opt$TyHGB < k & d_opt[[event_var]] == 1, na.rm = TRUE)
  event_t2 <- sum(d_opt$TyHGB >= k & d_opt[[event_var]] == 1, na.rm = TRUE)
  
  data.frame(
    Outcome = outcome_name, 
    Model = c("Standard linear model", 
              "Two-piecewise model (Slope evaluation)", 
              sprintf("  TyHGB < %.1f (Events: %d)", k, event_t1),
              sprintf("  TyHGB >= %.1f (Events: %d)", k, event_t2), 
              "  P for LRT",
              "Dichotomized by Threshold (Clinical HR)",
              sprintf("  Low Risk (< %.1f)", k),
              sprintf("  High Risk (>= %.1f)", k)),
    `HR (95% CI)` = c(hr_lin, "", hr_t1, hr_t2, "", "", "Ref.", hr_bin), 
    `P value` = c(p_lin, "", p_t1, p_t2, lrt_p_str, "", "-", p_bin),
    check.names = FALSE
  )
}

df_thresh <- bind_rows(run_piecewise("status_acm", "All-Cause Mortality"), run_piecewise("status_cvm", "Cardiovascular Mortality"))
df_thresh %>% 
  gt(groupname_col = "Outcome") %>% 
  tab_options(row_group.font.weight = "bold", row_group.background.color = "#E8F4F0") %>% 
  cols_align(align = "left", columns = 1) %>%
  tab_style(
    style = list(cell_text(weight = "bold", color = "black")),
    locations = cells_body(columns = `HR (95% CI)`, rows = grepl("High Risk", Model))
  )
```

## 11. Subgroup analyses

```{r}
#| label: fig-subgroup
#| fig-cap: "Figure 5: Subgroup analyses for the association between TyHGB index and mortality risk"
#| fig-width: 22
#| fig-height: 12

df_sub <- df_final %>%
  mutate(
    Age_group = case_when(RIDAGEYR < 40 ~ "18-39", RIDAGEYR >= 40 & RIDAGEYR < 60 ~ "40-59", RIDAGEYR >= 60 ~ ">=60"),
    Gender = ifelse(RIAGENDR == 1, "Male", "Female"),
    Hyperten_cat = ifelse(hyperten == 1, "Yes", "No")
  ) %>%
  mutate(
    Age_group = factor(Age_group, levels = c("18-39", "40-59", ">=60")),
    Gender = factor(Gender, levels = c("Male", "Female")),
    Hyperten_cat = factor(Hyperten_cat, levels = c("Yes", "No"))
  )

sub_design <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA, weights = ~WTSAF2YR, nest = TRUE, data = df_sub)
all_adj_vars <- unlist(strsplit(covs_str, " \\+ "))

var_list <- list(
  "Age" = list(col = "Age_group", rm_cov = "RIDAGEYR"),
  "Gender" = list(col = "Gender", rm_cov = "RIAGENDR"),
  "Race" = list(col = "RIDRETH1", rm_cov = "RIDRETH1"),
  "Hypertension" = list(col = "Hyperten_cat", rm_cov = "hyperten")
)

generate_subgroup_data <- function(event_var) {
  res_list <- list()
  for (v_name in names(var_list)) {
    col_name <- var_list[[v_name]]$col
    rm_cov <- var_list[[v_name]]$rm_cov
    curr_covs <- if(!is.na(rm_cov)) setdiff(all_adj_vars, rm_cov) else all_adj_vars
    covs_fmla <- paste(curr_covs, collapse = " + ")

    form_inter <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB *", col_name, "+", covs_fmla))
    fit_inter <- suppressWarnings(tryCatch(svycoxph(form_inter, design = sub_design), error = function(e) NULL))
    
    p_inter <- NA
    if(!is.null(fit_inter)) {
      p_inter <- suppressWarnings(tryCatch({ regTermTest(fit_inter, as.formula(paste("~ TyHGB:", col_name)))$p[1] }, error = function(e) NA))
    }
    p_inter_str <- ifelse(is.na(p_inter), "N/A", ifelse(p_inter < 0.001, "<0.001", sprintf("%.3f", p_inter)))
    
    res_list[[length(res_list) + 1]] <- data.frame(
      Variables = v_name, Subgroups = "", Event = "", ` ` = paste(rep(" ", 30), collapse = ""),
      `HR(95%CI)` = "", `P value` = "", `P for interaction` = p_inter_str,
      est = NA, lower = NA, upper = NA, check.names = FALSE, stringsAsFactors = FALSE
    )

    lvls <- levels(df_sub[[col_name]])
    for (lvl in lvls) {
      ev_count <- sum(df_sub[[col_name]] == lvl & df_sub[[event_var]] == 1, na.rm = TRUE)
      d_sub <- suppressMessages(suppressWarnings(subset(sub_design, get(col_name) == lvl)))
      form_sub <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB +", covs_fmla))
      fit_sub <- suppressWarnings(tryCatch(svycoxph(form_sub, design = d_sub), error = function(e) NULL))
      
      if (!is.null(fit_sub)) {
        sm <- summary(fit_sub)
        hr <- sm$conf.int[1, "exp(coef)"]
        ci_l <- sm$conf.int[1, "lower .95"]
        ci_u <- sm$conf.int[1, "upper .95"]
        pval <- sm$coefficients[1, "Pr(>|z|)"]
        if(!is.na(hr) && hr > 100) { hr <- NA; ci_l <- NA; ci_u <- NA }
        if(!is.na(hr)) {
          hr_str <- sprintf("%.3f (%.3f, %.3f)", hr, ci_l, ci_u)
          pval_str <- ifelse(pval < 0.001, "<0.001", sprintf("%.3f", pval))
        } else {
          hr_str <- "N/A"; pval_str <- "N/A"
        }
      } else {
        hr <- NA; ci_l <- NA; ci_u <- NA
        hr_str <- "N/A"; pval_str <- "N/A"
      }
      
      res_list[[length(res_list) + 1]] <- data.frame(
        Variables = "", Subgroups = paste0("      ", lvl), Event = as.character(ev_count),
        ` ` = paste(rep(" ", 30), collapse = ""), `HR(95%CI)` = hr_str, `P value` = pval_str, 
        `P for interaction` = "", est = hr, lower = ci_l, upper = ci_u,
        check.names = FALSE, stringsAsFactors = FALSE
      )
    }
  }
  return(do.call(rbind, res_list))
}

draw_forest_plot <- function(dt) {
  fill_colors <- c()
  current_color <- "#E8F4F0" 
  for (i in 1:nrow(dt)) {
    if (dt$Variables[i] != "") current_color <- ifelse(current_color == "white", "#E8F4F0", "white")
    fill_colors <- c(fill_colors, current_color)
  }
  
  tm <- forest_theme(
    base_size = 11, refline_gp = gpar(col = "black", lty = "dashed"), 
    arrow_type = "closed", arrow_label_just = "end", ci_pch = 15,
    ci_col = "#E64B35", ci_fill = "#E64B35", ci_alpha = 1, ci_lty = 1, ci_lwd = 1.5, ci_Theight = 0.2,
    core = list(bg_params = list(fill = fill_colors))
  )
  
  p <- forest(
    data = dt[, c("Variables", "Subgroups", "Event", " ", "HR(95%CI)", "P value", "P for interaction")],
    est = dt$est, lower = dt$lower, upper = dt$upper, ci_column = 4, ref_line = 1, arrow_lab = c("Low risk", "High Risk"),
    xlim = c(0.7, 1.2), clip = c(0.7, 1.2), ticks_at = c(0.7, 0.9, 1.0, 1.2), theme = tm
  )
  p <- edit_plot(p, row = 1:nrow(dt), col = 1, part = "body", gp = gpar(fontface = "bold"))
  p <- add_border(p, part = "header", row = 1, where = "top", gp = gpar(lwd = 1.5, col = "black"))
  p <- add_border(p, part = "header", row = 1, where = "bottom", gp = gpar(lwd = 1.5, col = "black"))
  p <- add_border(p, part = "body", row = nrow(dt), where = "bottom", gp = gpar(lwd = 1.5, col = "black"))
  return(p)
}

dt_acm <- generate_subgroup_data("status_acm")
p_acm <- draw_forest_plot(dt_acm)
dt_cvm <- generate_subgroup_data("status_cvm")
p_cvm <- draw_forest_plot(dt_cvm)

final_forest <- wrap_elements(full = p_acm) / wrap_elements(full = p_cvm)
final_forest <- final_forest + plot_annotation(tag_levels = 'A', tag_prefix = '(', tag_suffix = ')') & theme(plot.tag = element_text(size = 22, face = "bold")) 
final_forest
```

## 12. Detailed Mediation Analysis

```{r}
#| label: tbl-mediation
#| tbl-cap: "Supplemental Table 5: Detailed mediation analysis of TyHGB on ACM and CVM via Uric Acid and WBC count"

med_vars <- c("LBXSUA" = "Uric Acid", "LBXWBCSI" = "WBC Count")

run_sobel_med <- function(event_var, outcome_label) {
  res_list <- list()
  for(v in names(med_vars)) {
    d_clean <- df_final[!is.na(df_final[[v]]), ]
    des <- svydesign(id=~SDMVPSU, strata=~SDMVSTRA, weights=~WTSAF2YR, nest=TRUE, data=d_clean)
    
    fit_a <- svyglm(as.formula(paste(v, "~ TyHGB +", covs_str)), design = des)
    a <- coef(fit_a)["TyHGB"]; sa <- sqrt(vcov(fit_a)["TyHGB", "TyHGB"]) 
    
    fit_b <- svycoxph(as.formula(paste("Surv(time_months,", event_var, ") ~ TyHGB +", v, "+", covs_str)), design = des)
    b <- coef(fit_b)[v]; sb <- sqrt(vcov(fit_b)[v, v]) 
    c_prime <- coef(fit_b)["TyHGB"]; sc_prime <- sqrt(vcov(fit_b)["TyHGB", "TyHGB"])
    
    fit_c <- svycoxph(as.formula(paste("Surv(time_months,", event_var, ") ~ TyHGB +", covs_str)), design = des)
    c_tot <- coef(fit_c)["TyHGB"]; sc_tot <- sqrt(vcov(fit_c)["TyHGB", "TyHGB"])
    
    ab <- a * b; seb <- sqrt(a^2 * sb^2 + b^2 * sa^2)
    z_ab <- ab / seb; p_ab <- 2 * (1 - pnorm(abs(z_ab)))
    
    prop_med <- (ab / c_tot) * 100
    if(prop_med < 0) prop_med <- 0
    
    fmt <- function(est, se) sprintf("%.3f (%.3f to %.3f)", est, est - 1.96*se, est + 1.96*se)
    fmt_p <- function(p) ifelse(p < 0.001, "<0.001", sprintf("%.3f", p))
    p_ade <- summary(fit_b)$coef["TyHGB", "Pr(>|z|)"]
    
    res_list[[length(res_list)+1]] <- data.frame(
      Outcome = outcome_label, Mediator = med_vars[v],
      `ACME (95% CI)` = fmt(ab, seb), `P (ACME)` = fmt_p(p_ab),
      `ADE (95% CI)` = fmt(c_prime, sc_prime), `P (ADE)` = fmt_p(p_ade),
      `Prop. Mediated (%)` = sprintf("%.2f%%", prop_med), check.names = FALSE
    )
  }
  bind_rows(res_list)
}

df_med_tbl <- bind_rows(run_sobel_med("status_acm", "All-Cause Mortality"), run_sobel_med("status_cvm", "Cardiovascular Mortality"))
df_med_tbl %>% gt(groupname_col = "Outcome") %>% tab_options(row_group.font.weight = "bold", row_group.background.color = "#E8F4F0") %>% cols_align(align = "center") %>% cols_align(align = "left", columns = 1)
```

## 13. Construction of Nomograms

```{r}
#| label: fig-nomogram
#| fig-cap: "Figure 6: Nomograms predicting 3-, 5-, and 10-year survival probabilities for ACM (A) and CVM (B)"
#| fig-width: 16
#| fig-height: 18

model_vars <- c("TyHGB", "RIDAGEYR", "RIAGENDR", "RIDRETH1", "hyperten", "AST_ALT_ratio")
sys_vars <- c("time_months", "status_acm", "status_cvm", "event_cr", "WTSAF2YR")

df_nomo_rms <- df_final %>% select(all_of(c(sys_vars, model_vars))) %>% drop_na() %>% as.data.frame() 

df_nomo_rms$RIAGENDR <- factor(df_nomo_rms$RIAGENDR, levels = c(1, 2), labels = c("Male", "Female"))
df_nomo_rms$hyperten <- factor(df_nomo_rms$hyperten, levels = c(0, 1), labels = c("No", "Yes"))
df_nomo_rms$RIDRETH1 <- as.factor(df_nomo_rms$RIDRETH1)

Hmisc::label(df_nomo_rms$TyHGB)    <- "TyHGB Index"
Hmisc::label(df_nomo_rms$RIDAGEYR) <- "Age (years)"
Hmisc::label(df_nomo_rms$RIAGENDR) <- "Gender"
Hmisc::label(df_nomo_rms$RIDRETH1) <- "Race/Ethnicity"
Hmisc::label(df_nomo_rms$hyperten) <- "Hypertension"
Hmisc::label(df_nomo_rms$AST_ALT_ratio) <- "AST/ALT Ratio"

dd <- datadist(df_nomo_rms)
options(datadist = "dd")

form_acm <- as.formula(paste("Surv(time_months, status_acm) ~ TyHGB +", covs_str))
fit_acm_nomo <- cph(form_acm, data = df_nomo_rms, x = TRUE, y = TRUE, surv = TRUE, time.inc = 120, weights = df_nomo_rms$WTSAF2YR)
surv_acm <- Survival(fit_acm_nomo)
surv3_acm <- function(lp) surv_acm(36, lp)
surv5_acm <- function(lp) surv_acm(60, lp)
surv10_acm <- function(lp) surv_acm(120, lp)

prob_scale_acm <- c(0.95, 0.90, 0.80, 0.70, 0.60, 0.50)
nom_acm <- nomogram(fit_acm_nomo, fun = list(surv3_acm, surv5_acm, surv10_acm),
                    funlabel = c("3-Year ACM Survival", "5-Year ACM Survival", "10-Year ACM Survival"),
                    fun.at = prob_scale_acm, lp = FALSE)

df_nomo_rms$event_cr_fg <- factor(df_nomo_rms$event_cr, levels = c(0, 1, 2), labels = c("censor", "CVM", "Other_Death"))
fg_data_nomo <- finegray(Surv(time_months, event_cr_fg) ~ ., data = df_nomo_rms, etype = "CVM")
fg_data_nomo$final_wt <- fg_data_nomo$WTSAF2YR * fg_data_nomo$fgwt

Hmisc::label(fg_data_nomo$TyHGB)    <- "TyHGB Index"
Hmisc::label(fg_data_nomo$RIDAGEYR) <- "Age (years)"
Hmisc::label(fg_data_nomo$RIAGENDR) <- "Gender"
Hmisc::label(fg_data_nomo$RIDRETH1) <- "Race/Ethnicity"
Hmisc::label(fg_data_nomo$hyperten) <- "Hypertension"
Hmisc::label(fg_data_nomo$AST_ALT_ratio) <- "AST/ALT Ratio"

options(datadist = "dd") 

form_cvm <- as.formula(paste("Surv(fgstart, fgstop, fgstatus) ~ TyHGB +", covs_str))
fit_cvm_nomo <- cph(form_cvm, data = fg_data_nomo, x = TRUE, y = TRUE, surv = TRUE, time.inc = 120, weights = fg_data_nomo$final_wt)
surv_cvm <- Survival(fit_cvm_nomo)
surv3_cvm <- function(lp) surv_cvm(36, lp)
surv5_cvm <- function(lp) surv_cvm(60, lp)
surv10_cvm <- function(lp) surv_cvm(120, lp)

prob_scale_cvm <- c(0.99, 0.95, 0.90, 0.80, 0.70)
nom_cvm <- nomogram(fit_cvm_nomo, fun = list(surv3_cvm, surv5_cvm, surv10_cvm),
                    funlabel = c("3-Year CVM Survival", "5-Year CVM Survival", "10-Year CVM Survival"),
                    fun.at = prob_scale_cvm, lp = FALSE)

par(mfrow=c(2,1), mar=c(5, 6, 4, 3) + 0.1)
plot(nom_acm, cex.axis=0.85, cex.var=0.9, xfrac=0.45)
title("A. Nomogram for All-Cause Mortality (ACM)", adj = 0, line = 1.5, cex.main=1.4)
plot(nom_cvm, cex.axis=0.85, cex.var=0.9, xfrac=0.45)
title("B. Nomogram for Cardiovascular Mortality (CVM) - Fine-Gray Model", adj = 0, line = 1.5, cex.main=1.4)
```

## 14. Calibration Plots

```{r}
#| label: fig-calibration
#| fig-cap: "Figure 7: Calibration plots comparing predicted vs observed 10-years"
#| fig-width: 14
#| fig-height: 6

set.seed(123)
cal_acm <- calibrate(fit_acm_nomo, cmethod='KM', method="crossvalidation", B=10, u=120)

form_cvm_proxy <- as.formula(paste("Surv(time_months, event_cr == 1) ~ TyHGB +", covs_str))
fit_cvm_cal_proxy <- cph(form_cvm_proxy, data = df_nomo_rms, x = TRUE, y = TRUE, surv = TRUE, time.inc = 120, weights = df_nomo_rms$WTSAF2YR)
cal_cvm <- calibrate(fit_cvm_cal_proxy, cmethod='KM', method="crossvalidation", B=10, u=120)

plot_cal_ggplot <- function(cal_obj, title_str, color_theme, show_ylab = TRUE) {
  df_cal <- data.frame(pred = cal_obj[, "mean.predicted"], obs = cal_obj[, "KM"], obs_corr = cal_obj[, "KM.corrected"])
  max_val <- min(max(c(df_cal$pred, df_cal$obs_corr), na.rm = TRUE) + 0.05, 1) 
  p <- ggplot(df_cal, aes(x = pred)) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray50", linewidth = 0.8) +
    geom_line(aes(y = obs, color = "Apparent (Original)"), linetype = "dotted", linewidth = 1) +
    geom_point(aes(y = obs, color = "Apparent (Original)"), size = 2) +
    geom_line(aes(y = obs_corr, color = "Bias-corrected (Cross-validated)"), linewidth = 1.2) +
    geom_point(aes(y = obs_corr, color = "Bias-corrected (Cross-validated)"), size = 1.5) +
    scale_color_manual(name = "Model Performance:", values = c("Apparent (Original)" = "black", "Bias-corrected (Cross-validated)" = color_theme)) +
    coord_cartesian(xlim = c(0, max_val), ylim = c(0, max_val)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
    labs(title = title_str, x = "Predicted 10-Year Probability", y = ifelse(show_ylab, "Observed Actual Proportion", "")) +
    theme_classic() + 
    theme(plot.title = element_text(face = "bold", size = 14), axis.title = element_text(size = 12, face = "bold"),
          axis.text = element_text(size = 11, color = "black"), legend.position = c(0.35, 0.85), 
          legend.background = element_rect(fill = alpha("white", 0.9), color = NA),
          legend.text = element_text(size = 10), legend.title = element_text(size = 10, face = "bold", color = "gray30"))
  return(p)
}

p_cal_acm <- plot_cal_ggplot(cal_acm, "A. 10-Year ACM Calibration", "#E64B35", show_ylab = TRUE) 
p_cal_cvm <- plot_cal_ggplot(cal_cvm, "B. 10-Year CVM Calibration", "#4DBBD5", show_ylab = FALSE) 
p_cal_acm | p_cal_cvm
```

# 15. Decision Curve Analysis (DCA)

```{r}
#| label: fig-dca
#| fig-cap: "Figure 8: Decision Curve Analysis (DCA) demonstrating the net benefit of the TyHGB clinical model at 10 years"
#| fig-width: 14
#| fig-height: 6

df_dca <- as.data.frame(df_nomo_rms)
surv10_acm_cal <- Survival(fit_acm_nomo)
df_nomo_rms$prob_acm_10 <- 1 - surv10_acm_cal(120, predict(fit_acm_nomo, newdata = df_dca, type="lp"))
surv10_cvm_cal <- Survival(fit_cvm_nomo)
df_nomo_rms$prob_cvm_10 <- 1 - surv10_cvm_cal(120, predict(fit_cvm_nomo, newdata = df_dca, type="lp"))

plot_beautiful_dca <- function(form, event_time, title_str, line_color, var_name) {
  lbl_list <- list(); lbl_list[[var_name]] <- "TyHGB Model"
  dca_obj <- dca(form, data = df_nomo_rms, time = event_time, label = lbl_list)
  df <- as_tibble(dca_obj) %>% dplyr::filter(!is.na(net_benefit))
  
  best_strat <- df %>% dplyr::group_by(threshold) %>% dplyr::slice_max(order_by = net_benefit, n = 1, with_ties = FALSE) %>% dplyr::ungroup() %>% dplyr::arrange(threshold)
  best_strat <- best_strat %>% dplyr::mutate(group = cumsum(label != dplyr::lag(label, default = dplyr::first(label))))
  regions <- best_strat %>% dplyr::group_by(group, label) %>% dplyr::summarize(x_start = min(threshold), x_end = max(threshold), x_mid = mean(threshold), .groups = "drop") %>% dplyr::filter((x_end - x_start) > 0.02) 
  
  max_nb <- max(df$net_benefit, na.rm = TRUE)
  y_min <- -max_nb * 0.12; strip_y <- -max_nb * 0.06 
  
  p <- ggplot() +
    geom_rect(data = regions, aes(xmin = x_start, xmax = x_end, ymin = y_min, ymax = 0, fill = label), alpha = 0.2) +
    geom_text(data = regions, aes(x = x_mid, y = strip_y, label = label), color = "gray20", size = 3.5, fontface = "bold", vjust = 0.5) +
    geom_line(data = df, aes(x = threshold, y = net_benefit, color = label, linetype = label), linewidth = 1.2) +
    scale_color_manual(values = c("Treat All" = "gray50", "Treat None" = "black", "TyHGB Model" = line_color)) +
    scale_fill_manual(values = c("Treat All" = "gray50", "Treat None" = "black", "TyHGB Model" = line_color)) +
    scale_linetype_manual(values = c("Treat All" = "solid", "Treat None" = "solid", "TyHGB Model" = "solid")) +
    coord_cartesian(xlim = c(0, max(df$threshold)), ylim = c(y_min, max_nb * 1.05)) +
    scale_x_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
    labs(title = title_str, x = "Threshold Probability", y = "Net Benefit") + theme_classic() +
    theme(plot.title = element_text(face = "bold", size = 14), axis.title = element_text(face = "bold", size = 12),
          axis.text = element_text(size = 11, color = "black"), axis.text.x = element_text(margin = margin(t = 5)), 
          legend.position = c(0.85, 0.85), legend.title = element_blank(), legend.text = element_text(size = 11, face = "bold"),
          legend.background = element_rect(fill = alpha("white", 0.8), color = "gray80", linewidth = 0.5), panel.grid.major.y = element_line(color = "gray90", linetype = "dotted")) + guides(fill = "none") 
  return(p)
}

p_dca_acm <- plot_beautiful_dca(Surv(time_months, status_acm) ~ prob_acm_10, 120, "A. 10-Year ACM Decision Curve", "#E64B35", "prob_acm_10")
p_dca_cvm <- plot_beautiful_dca(Surv(time_months, event_cr == 1) ~ prob_cvm_10, 120, "B. 10-Year CVM Decision Curve", "#4DBBD5", "prob_cvm_10")
p_dca_acm | p_dca_cvm
```

## 16. Multiple Imputation Stability Check (m = 20)

```{r}
#| label: fig-mice-stability
#| fig-cap: "Supplemental Figure: Stability of the TyHGB prognostic value (High vs Low based on threshold) across 20 imputed datasets"
#| fig-width: 14
#| fig-height: 8

imp_20 <- mice(df_step1[, vars_to_impute], m = 20, method = 'pmm', seed = 123, printFlag = FALSE)

get_mice_hr_highlow <- function(event_var, threshold, title) {
  res_df <- data.frame()
  estimates <- c(); vars <- c()
  
  for(i in 1:20) {
    d_i <- df_step1
    d_i[, vars_to_impute] <- complete(imp_20, i)
    d_i <- d_i %>% mutate(
      HSI = 8*(LBXSATSI/LBXSASSI) + BMXBMI + ifelse(RIAGENDR==2,2,0) + ifelse(diabetes==1,2,0),
      steatosis = ifelse(HSI > 36, 1, 0),
      cm_risk = ifelse(BMXBMI>=25 | (RIAGENDR==1 & BMXWAIST>=94) | (RIAGENDR==2 & BMXWAIST>=80) | LBDSGLSI>=5.55 | diabetes==1 | hyperten==1 | LBXTR>=150 | (RIAGENDR==1 & LBDHDD<40) | (RIAGENDR==2 & LBDHDD<50), 1, 0),
      is_masld = ifelse(steatosis==1 & cm_risk==1, 1, 0),
      TyHGB = (LBXTR/LBDHDD) + (0.7*LBDSGLSI) + (0.1*BMXBMI),
      AST_ALT_ratio = LBXSASSI / LBXSATSI,
      status_acm = ifelse(mortstat==1, 1, 0),
      status_cvm = ifelse(mortstat==1 & ucod_leading %in% c("001","005"), 1, 0),
      time_months = permth_int
    ) %>% filter(is_masld == 1, (is.na(RIDEXPRG) | RIDEXPRG != 1), !is.na(mortstat), !is.na(time_months), eligstat == 1)
    
    d_i$hyperten <- as.numeric(as.character(d_i$hyperten))
    d_i$TyHGB_High <- ifelse(d_i$TyHGB >= threshold, 1, 0)
    
    des_i <- svydesign(id=~SDMVPSU, strata=~SDMVSTRA, weights=~WTSAF2YR, nest=TRUE, data=d_i)
    fit_i <- svycoxph(as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_High +", covs_str)), design = des_i)
    
    estimates[i] <- coef(fit_i)["TyHGB_High"]
    vars[i] <- vcov(fit_i)["TyHGB_High", "TyHGB_High"]
    
    res_df <- rbind(res_df, data.frame(Imputation = paste("Imputation", i), HR = exp(estimates[i]), 
                                       LCI = exp(estimates[i] - 1.96*sqrt(vars[i])), UCI = exp(estimates[i] + 1.96*sqrt(vars[i]))))
  }
  
  Q_bar <- mean(estimates); U_bar <- mean(vars); B <- var(estimates); T_var <- U_bar + (1 + 1/20) * B
  
  res_df <- rbind(res_df, data.frame(Imputation = "Pooled (Rubin's Rules)", HR = exp(Q_bar), LCI = exp(Q_bar - 1.96*sqrt(T_var)), UCI = exp(Q_bar + 1.96*sqrt(T_var))))
  res_df$Imputation <- factor(res_df$Imputation, levels = rev(res_df$Imputation))
  
  ggplot(res_df, aes(x = HR, y = Imputation)) +
    geom_vline(xintercept = 1, linetype = "dashed", color = "black") +
    geom_errorbarh(aes(xmin = LCI, xmax = UCI), height = 0.2, color = "#0055A4", linewidth = 1.2) +
    geom_point(size = 4.5, color = ifelse(res_df$Imputation == "Pooled (Rubin's Rules)", "#E64B35", "#0055A4"), 
               shape = ifelse(res_df$Imputation == "Pooled (Rubin's Rules)", 18, 16)) +
    theme_classic() + labs(title = title, x = sprintf("Hazard Ratio (TyHGB >= %.1f vs < %.1f)", threshold, threshold), y = "") +
    theme(plot.title = element_text(face = "bold", size = 14), axis.title = element_text(face="bold"), axis.text = element_text(size = 9, color="black", face="bold"))
}

# TODO: ĐIỀN ĐIỂM UỐN k TỪ BƯỚC 10 VÀO ĐÂY (VÍ DỤ TẠM LÀ 12.1 VÀ 11.9)
nguong_acm <- 12.1 
nguong_cvm <- 11.9

p_mice_acm <- get_mice_hr_highlow("status_acm", nguong_acm, paste("A. ACM Models Stability (Threshold =", nguong_acm, ")"))
p_mice_cvm <- get_mice_hr_highlow("status_cvm", nguong_cvm, paste("B. CVM Models Stability (Threshold =", nguong_cvm, ")"))

p_mice_acm | p_mice_cvm
```

## 17. E-Value Analysis

```{r}
#| label: fig-evalue
#| fig-cap: "Supplemental Figure: E-value curves for the High vs Low TyHGB index on mortality"
#| fig-width: 14
#| fig-height: 6

get_evalue <- function(est) {
  if (is.na(est)) return(NA); if (est < 1) est <- 1 / est; return(est + sqrt(est * (est - 1)))
}
get_evalue_ci <- function(est, limit) {
  if (is.na(est) || is.na(limit)) return(NA)
  if (est > 1 && limit <= 1) return(1); if (est < 1 && limit >= 1) return(1)
  if (limit < 1) limit <- 1 / limit; return(limit + sqrt(limit * (limit - 1)))
}

plot_evalue_highlow <- function(event_var, threshold, title) {
  df_eva <- df_final; df_eva$TyHGB_High <- ifelse(df_eva$TyHGB >= threshold, 1, 0)
  des_eva <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA, weights = ~WTSAF2YR, nest = TRUE, data = df_eva)
  
  form <- as.formula(paste("Surv(time_months, ", event_var, ") ~ TyHGB_High +", covs_str))
  fit <- svycoxph(form, design = des_eva)
  sm <- summary(fit)
  
  hr <- as.numeric(sm$conf.int["TyHGB_High", 1])
  lci <- as.numeric(sm$conf.int["TyHGB_High", 3])
  e_point <- get_evalue(hr); e_lower <- get_evalue_ci(hr, lci)
  
  rr_eu <- seq(1.001, 20, length.out = 1000) 
  rr_ud_point <- (hr * rr_eu - hr) / (rr_eu - hr)
  rr_ud_point <- ifelse(rr_eu > hr & rr_ud_point >= 1, rr_ud_point, NA)
  
  df_curve <- data.frame(rr_eu = rr_eu, rr_ud_point = rr_ud_point)
  
  if (e_lower > 1) {
    rr_ud_lower <- (lci * rr_eu - lci) / (rr_eu - lci)
    df_curve$rr_ud_lower <- ifelse(rr_eu > lci & rr_ud_lower >= 1, rr_ud_lower, NA)
  }
  col_point <- "#C2185B"; col_lower <- "#008080"
  axis_limit <- max(e_point * 2.2, e_lower * 3, 4.0) 
  
  p <- ggplot(df_curve, aes(x = rr_eu)) +
    geom_line(aes(y = rr_ud_point, color = "Point Estimate"), linewidth = 1.5, linetype = "solid", na.rm = TRUE)
  
  if (e_lower > 1) {
    p <- p + geom_line(aes(y = rr_ud_lower, color = "Lower Confidence Limit"), linewidth = 1.5, linetype = "solid", na.rm = TRUE) +
      geom_point(aes(x = e_lower, y = e_lower), color = col_lower, size = 4.5) +
      annotate("text", x = e_lower + 0.08, y = e_lower + 0.12, label = sprintf("E-value (LCI) = %.2f", e_lower), fontface="bold", color=col_lower, size=4, hjust = 0, vjust = 1)
  }
  
  p <- p + geom_point(aes(x = e_point, y = e_point), color = col_point, size = 4.5) +
    annotate("text", x = e_point + 0.08, y = e_point + 0.08, label = sprintf("E-value = %.2f", e_point), fontface="bold", color=col_point, size=4, hjust = 0, vjust = 0) +
    scale_color_manual(values = c("Point Estimate" = col_point, "Lower Confidence Limit" = col_lower)) +
    coord_cartesian(xlim = c(1, axis_limit), ylim = c(1, axis_limit)) +
    labs(title = title, x = expression(bold(RR[EU])~"(Exposure-Confounder Effect)"), y = expression(bold(RR[UD])~"(Confounder-Outcome Effect)")) +
    theme_classic() + 
    theme(legend.position = c(0.75, 0.85), legend.title = element_blank(), legend.text = element_text(face = "bold", size = 11),
          plot.title = element_text(face="bold", size = 14), axis.title = element_text(face="bold", size = 12),
          axis.text = element_text(color = "black", size = 11), legend.background = element_rect(color="black", linewidth = 0.5), panel.grid.minor = element_blank(), panel.grid.major = element_blank())
  return(p)
}

# NHỚ ĐỔI THRESHOLD Ở ĐÂY CHO KHỚP BƯỚC 10
p_ev_acm <- plot_evalue_highlow("status_acm", nguong_acm, paste("A. E-value for ACM (Threshold =", nguong_acm, ")"))
p_ev_cvm <- plot_evalue_highlow("status_cvm", nguong_cvm, paste("B. E-value for CVM (Threshold =", nguong_cvm, ")"))
p_ev_acm | p_ev_cvm
```

